イーサリアム: 安全な分散型汎用トランザクション台帳\\ \smaller \textbf{{Berlin version \YellowPaperVersionNumber}}

### 2022-07-19 Paper.tex
[WIP] error: Unicode-character

The source of this paper is maintained at \url{https://github.com/ethereum/yellowpaper/}. An auto-generated PDF is located at \url{https://ethereum.github.io/yellowpaper/paper.pdf}.

>>>>

% The source of this paper is maintained at \url{https://github.com/ethereum/yellowpaper/}. An auto-generated PDF is located at \url{https://ethereum.github.io/yellowpaper/paper.pdf}.

本論文の出典は、以下のサイトで管理されています。

[https://github.com/ethereum/yellowpaper/.](https://github.com/ethereum/yellowpaper/)

自動生成されたPDFは以下の場所にあります。

[https://ethereum.github.io/yellowpaper/paper.pdf](https://ethereum.github.io/yellowpaper/paper.pdf)
